Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-02-15 main.tex
completed revisions to Sect 4.  Fixed up a couple of acronyms

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
We furthermore follow the star-by-star stellar yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods in a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work impacts our understanding of galactic chemical evolution on a species-by-species basis. {\bf the conclusion of this discussion should perhaps be mentioned.}
\end{abstract}

@@

%mm2 [if we were to keep the previous sentence, we'd need to segue like this.]
%   Nevertheless, we 
We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation. 
%mm2
  We include stellar feedback from stellar winds, core collapse and Type Ia supernovae,    
  photoelectric heating, and ionizing radiation.

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. self-consistent set of stellar yields. 
%mm2 
    We track yields from massive star stellar winds, AGB star winds, and supernovae. 
In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed 
%mm2
   distributions of
chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
%mm2 
This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. 
%mm2 [this is somehow redundant with the previous paragraph.  I have moved a few things up.]
% In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields
%to track yields from massive star stellar winds, AGB star winds, and supernovae. 
We describe each mode of our multi-channel feedback 
in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation
%mm2 
   in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the 
   results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. After this point, the molecular component dominates through the end of the simulation.

Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future works.

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values only. \ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the \ion{H}{1} ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It is unclear which of these two modes of feedback is more important in controlling star formation.

@@

The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}. However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}. In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \citet{Muratov2015} defining the mass outflow rate ($\dot{M}_{\rm outflow}$) at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
\begin{equation} \label{eq:dotM}
\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL.
\end{equation} 
We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. Generally, other works use long timescale measurements of the SFR ($\sim$~Gyr) to compute the mass loading factor. For consistency in these works, we use the 500~Myr average SFR for computing the mass loading factor. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time. This quickly declines towards larger radii, however, with minimal outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift. Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.

Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few. Using a fit provided in \citet{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find. These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison. We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly much smaller mass loading factors at 0.25 $R_{\rm vir}$.

@@

\subsection{Metal Evolution} 
\label{sec:chemical evolution}
\textbf{This section saw significant change. Removed previous mention of stellar abundances and species retention fractions. Much of below is new(ish)}

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. We define the metal mass loading factor as
\begin{equation}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions. For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but each increases, fluctuating around unity for the second half of the simulation. Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different value for their galaxies, a normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
\caption{Top: Metal mass loading factor at four radii over time (see text for how this is defined). Bottom: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time. After the first 20 Myr, supernova driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 40\% by the end of the simulation. Likewise, the CGM metal content is continually decreasing until the end of the simulation, from loss through the virial radius of the halo. Although the metal content of the ISM is gradually decreasing throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution. See Section~\ref{sec:obs_metals} for further discussion.
%\textbf{closing sentence}

@@

It is important to understand how metals from each source of stellar yields (stellar winds, AGB star winds, and supernovae) enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport must occur much more rapidly ($\sim 10^2$~Myr) than what is possible assuming transport at the cold gas sound speed ($\sim 1$~Gyr). This suggests either that metals are transported first through a hot phase or are driven through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}. How metal abundances vary in detail within these galaxies, beyond 1D radial profiles, and whether or not abundance distributions depend on the metal species is uncertain. It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.

We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, in addressing these questions with Fig~\ref{fig:metal_slices}. The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy. These serve to guide the eye in the lower panels, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K). The bottom panels give abundance ratios for oxygen and hydrogen (bottom left), nitrogen and hydrogen (bottom middle), and nitrogen and oxygen (bottom right).

\begin{figure*}
\centering
\includegraphics[width=0.32\linewidth]{number_density} 
\includegraphics[width=0.32\linewidth]{temperature}\\
\includegraphics[width=0.32\linewidth]{log_OH} 
\includegraphics[width=0.32\linewidth]{log_NH}
\includegraphics[width=0.32\linewidth]{log_NO}
\caption{Five slices in the mid-place of our dwarf galaxy at an arbitrary time demonstrating the power of our chemical evolution model. We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right). We caution against making direct comparisons of these images to observed abundances of dwarf galaxies, as we do not capture a cosmologically realistic chemical evolution in these relatively short ($< 1$~Gyr) simulations. This will be addressed in future work. \textbf{(AE: need to adjust axis label size)}}
\label{fig:metal_slices}
\end{figure*}

>>>>

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive and asymptotic giant branch stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
We furthermore follow the star-by-star stellar yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods in a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work impacts our understanding of galactic chemical evolution on a species-by-species basis. {\bf the conclusion of this discussion should perhaps be mentioned.}
\end{abstract}

@@

%mm2 [if we were to keep the previous sentence, we'd need to segue like this.]
%   Nevertheless, we 
We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation. 
%mm2
  We include stellar feedback from stellar winds, core collapse and Type Ia supernovae,    
  photoelectric heating, and ionizing radiation.

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. self-consistent set of stellar yields. 
%mm2 
    We track yields from massive and AGB star winds, and supernovae. 
In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed 
%mm2
   distributions of
chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
%mm2 
This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. 
%mm2 [this is somehow redundant with the previous paragraph.  I have moved a few things up.]
% In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields
%to track yields from massive star stellar winds, AGB star winds, and supernovae. 
We describe each mode of our multi-channel feedback 
in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation
%mm2 
   in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the 
   results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. After this point, the molecular component dominates through the end of the simulation.
%mm2 [remove para break]
Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.

%mm[new para]
These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. \ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the \ion{H}{1} ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It 
%mm2 is unclear 
   remains to be seen
which of these two modes of feedback is more important in controlling star formation.

@@

The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}. However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}. In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
\begin{equation} \label{eq:dotM}
\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
\end{equation} 
We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor. For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time. This quickly declines towards larger radii, however, with minimal outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift. Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.

Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few. Using a fit provided in \citet{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find. These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison. We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.

@@

\subsection{Metal Evolution} 
\label{sec:chemical evolution}
%mm2 \textbf{This section saw significant change. Removed previous mention of stellar abundances and species retention fractions. Much of below is new(ish)}

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. We define the metal mass loading factor as
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions. For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation. Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
\caption{Top: Metal mass loading factor (see Eq.~\ref{eq:eta-metal}) at radii of 0.1 ({\em black}), 0.2 ({\em purple}), 0.5 ({\em salmon pink}), and 1.0 $R_{\rm vir}$ ({\em yellow}) over time. Bottom: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time. After the first 20 Myr, supernova-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, reaching 40\% by the end of the simulation. Likewise, the CGM metal content continually decreases until the end of the simulation, from loss through the virial radius of the halo. Although the metal content of the ISM gradually decreases throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution. See Section~\ref{sec:obs_metals} for further discussion.
%\textbf{closing sentence}

@@

It is important to understand how metals from each source of stellar yields (massive and AGB stellar winds and supernovae) enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed. This suggests either that metals are transported first through a hot phase 
%mm2 
   with high sound speed, 
or by efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}. It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species. It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.

We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}. The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy. These serve to guide the eye in the lower panels, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K). The bottom panels give abundance ratios for oxygen and hydrogen (bottom left), nitrogen and hydrogen (bottom middle), and nitrogen and oxygen (bottom right).

\begin{figure*}
\centering
\includegraphics[width=0.32\linewidth]{number_density} 
\includegraphics[width=0.32\linewidth]{temperature}\\
\includegraphics[width=0.32\linewidth]{log_OH} 
\includegraphics[width=0.32\linewidth]{log_NH}
\includegraphics[width=0.32\linewidth]{log_NO}
\caption{Five slices in the mid-plane of our dwarf galaxy at an arbitrary time 
%mm2 [give the time]
  of {\bf XXX}~Myr after the start of star formation,
demonstrating the power of our chemical evolution model. We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right). We caution against making direct comparisons of these images to observed abundances of dwarf galaxies, as we do not capture a cosmologically realistic chemical evolution in these relatively short ($< 1$~Gyr) simulations. This will be addressed in future work. \textbf{(AE: need to adjust axis label size)}}
\label{fig:metal_slices}
\end{figure*}
